---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
library(tidyverse)

knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
body {font-family: Arial;}

h2 {color: #3775E6;}
```

## Patterns in Daily Phone Usage

This report explores patterns in phone usage based on observational data collected over multiple usage events. This analysis focuses on how long the phone is used, which apps are most frequently accessed, and the purpose of usage. 

```{r} 
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vSGoBBsl78Iq8wXST44xGAapxwXKHk7Dj1BHK0XvjbLkhc2-QgtUArefEilbYR5_ywZyQuJYCNLnsvD/pub?gid=2031172847&single=true&output=csv")

latest_data <- logged_data %>%
  rename(minutes = "How long did you use your phone during this usage event? (minutes)",
         App = "Which app did you primarily use",
         purpose = "What was the main purpose of this phone use?",
         time_of_day = "What time of day did this occur?",
         feeling = "How did you feel after using your phone?",
         extra_details = "Were there any noticeable distractions or additional details?")

``` 

The average phone usage time was `r mean(latest_data$minutes, na.rm = TRUE)` minutes. 

The max phone usage time was `r max(latest_data$minutes, na.rm = TRUE)` minutes

```{r}
ggplot(data = latest_data) +
  geom_bar(aes(x = App), fill = "#3775E6") +
  labs(title = "Which apps are used more frequently?",
       subtitle = "Comparing the frequency of different apps used during phone usage events",
       caption = "Source: Phone usage observation data",
       x = "App",
       y = "Number of usage events")
```

```{r}
ggplot(data = latest_data) +
  geom_bar(aes(x = purpose),fill = "#EE351B") +
  labs(title = "What are the phones mainly used for?",
       subtitle = "Comparing the purposes of phone usage across different events",
       caption = "Source: Phone usage observation data",
       x = "Purpose of use",
       y = "Number of usage events")
```

